Methodology for Assessing the State of the Practice for Domain X

### 2020-12-14 StateOfPractice/Methodology/Methodology.tex
Further edits to the introduciton section.

Given the importance of research software, scientists and engineers are pushing
for methods and tools to sustainably develop hiqh quality software.  This is
evident from the existence of such groups as the Software Sustainability
Institute (\href{https://www.software.ac.uk/} {SEI}) and Better Scientific
Software (\href{https://bssw.io/} {BSS}).  Groups such as these are necessary
for promoting sustainable practices because unfortunately the current
state-of-the-practice for research software often does not incorporate
state-of-the-art Software Engineering (SE) tools and methods
\citep{JohansonAndHasselbring2018}.  The lack of SE tools and methods
contributes to sustainability and reliability problems \citep{FaulkEtAl2009}.
Problems with the current state of the practice are evident from embarrassing
failures, like a retraction of derived molecular protein structures
\citep{Miller2006}, false reproduction of sonoluminescent fusion
\citep{PostAndVotta2005}, and fixing and then reintroducing the same error in a
large code base three times in 20 year \citep{MilewiczAndRaybourn2018}.  To
improve this situation, we need to first more fully understand the current state of
the practice for research software.

To understand the current quality of research software and to assist in
developing methods for measuring qualities, we will identify several domains
within research software and endeavour to summarize the current state of the
practice within those domains.  This ``state of the practice'' exercise will
build off of prior work on measuring/assessing the state of software development
practice in several research domains.  We will update the work that was done
previously for domains such as Geographic Information Systems
\citep{SmithEtAl2018_arXivGIS}, Mesh Generators \citep{SmithEtAl2016},
Seismology software \citep{SmithEtAl2018}, and Statistical software for
psychology \citep{SmithEtAl2018_StatSoft}.

In the previous project, we measured 30 software projects for each domain, but
the measures were relatively shallow.  With the re-boot we are refining the list
into a short list of the best projects for more detailed measurement.

>>>>

Given the importance of research software, scientists and engineers are pushing
for methods and tools to sustainably develop hiqh quality software.  This is
evident from the existence of such groups as the Software Sustainability
Institute (\href{https://www.software.ac.uk/} {SEI}) and Better Scientific
Software (\href{https://bssw.io/} {BSS}).  Sustainability promoting groups such
as these are necessary because unfortunately the current state-of-the-practice
for research software often does not incorporate state-of-the-art Software
Engineering (SE) tools and methods \citep{JohansonAndHasselbring2018}.  The lack
of SE tools and methods contributes to sustainability and reliability problems
\citep{FaulkEtAl2009}.  Problems with the current state of the practice are
evident from embarrassing failures, like a retraction of derived molecular
protein structures \citep{Miller2006}, false reproduction of sonoluminescent
fusion \citep{PostAndVotta2005}, and fixing and then reintroducing the same
error in a large code base three times in 20 year
\citep{MilewiczAndRaybourn2018}.  To improve this situation, we need to first
fully understand the current state of the practice for research software.

The purpose of our proposed methodology is to gain insight on how software
quality is impacted by the software development principles, processes and tools
currently used within research software communities.  Since research software is
so broad a category, we will reduce the scope of each application of the
methodology by applying it to a specific domain within research software.  This
``state of the practice for domain X'' exercise will build off of prior work on
measuring/assessing the state of software development practice in several
research domains.  We will update the work that was done previously for domains
such as Geographic Information Systems \citep{SmithEtAl2018_arXivGIS}, Mesh
Generators \citep{SmithEtAl2016}, Seismology software \citep{SmithEtAl2018}, and
Statistical software for psychology \citep{SmithEtAl2018_StatSoft}.

In the previous project, we measured 30 software projects for each domain, but
the measures were relatively shallow.  With this re-boot we are adding more
measures and experiments.  refining the list
into a short list of the best projects for more detailed measurement.  More details.
